EvoSwarm: A Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-08-21 draft.tex
Update draft.tex

However, when we compare the two options, we find some subtle differences: When
using one or two workers, using 5 populations takes less time in most cases. In
Table~\ref{tab:time} results with p-value of the two-tailed Wilcoxon
signed-ranks test was grater than the level of significance of 0.05 (i.e.,
accepting the null hypothesis of inequality) are marked in boldface. A reason
for this could be that when having more populations, the migration of
individuals takes more time from the bdyeginning to reach to all of them. For
instance, when a single worker has 10 populations, only after processing every
one of them, it will start receiving mixed populations. Although, in all cases,
and even with a single worker, populations are heterogeneous, individuals
resulting from the mixing of populations take more time to propagate. With four
workers, almost the same results can be achieved regardless of our selection
between five or ten populations. Also, there is not much difference between 4
and 8 workers, when using five populations, which might indicate that some
workers are idling while populations are being processed by other workers. In
general, we can observe that keeping a ratio between the number of workers and
populations a bit over 1:1 exploits better the computing resources available.
This also decreases the relation between the overhead needed to migrate and
process incoming and outgoing population and the total computing time: more
populations will need more time to do that.

>>>>

% However, when we compare the two options, we find some subtle differences: When
% using one or two workers, using 5 populations takes less time in most cases. In
% Table~\ref{tab:time} results with p-value of the two-tailed Wilcoxon
% signed-ranks test was grater than the level of significance of 0.05 (i.e.,
% accepting the null hypothesis of inequality) are marked in boldface. A reason
% for this could be that when having more populations, the migration of
% individuals takes more time from the bdyeginning to reach to all of them. For
% instance, when a single worker has 10 populations, only after processing every
% one of them, it will start receiving mixed populations. Although, in all cases,
% and even with a single worker, populations are heterogeneous, individuals
% resulting from the mixing of populations take more time to propagate. With four
% workers, almost the same results can be achieved regardless of our selection
% between five or ten populations. Also, there is not much difference between 4
% and 8 workers, when using five populations, which might indicate that some
% workers are idling while populations are being processed by other workers. In
% general, we can observe that keeping a ratio between the number of workers and
% populations a bit over 1:1 exploits better the computing resources available.
% This also decreases the relation between the overhead needed to migrate and
% process incoming and outgoing population and the total computing time: more
% populations will need more time to do that.
